Multi-level modeling with Openflexo/\FML

### 2022-03-25 4-technology.tex
typo
shorter code

To meet the \mlpc, we have decided to use the language infrastructure of
model federation approach~\parencite{Golra2016-federation}. \emph{Model
  federation} is a way to assemble models using some kind of
low-coupling links. It was initially  formulated to respond to the \OMG's RFP
Semantic Modeling for Information Federation~\parencite{simf}. In
contrast to approaches that compose metamodels into a single large
metamodel grouping all needed entities, model federation build links
between models and metamodels (even through levels) to make ``things''
work together. As an illustration of this feature, we developed a
free-modeling editor presented
in~\parencite{models2016-freemodel} that frees the designer from the bonds of
model/metamodel conformity. Another notable feature of
this approach is the strong decoupling among tools that remain usable
after federations are made.
So to provide an adaptable framework, we have developed a flexible modeling language to provide modeling features without strict modeling levels. In a federation, the targeted modeling approaches can be unknown at the beginning and also can integrate several modeling levels.

@@

      // A basic constructor
      create(String name) { super(name); }
      // Encodes execution of task
      execute() {
        log("Execute task "+name);
        ...
      }
      // Other properties and behaviours of the
      // BPMNTask concept
      ...

    }

>>>>

To meet the \mlpc, we have decided to use the language infrastructure of
model federation approach~\parencite{Golra2016-federation}. \emph{Model
  federation} is a way to assemble models using some kind of
low-coupling links. It was initially  formulated to respond to the \OMG's RFP
Semantic Modeling for Information Federation~\parencite{simf}. In
contrast to approaches that compose metamodels into a single large
metamodel grouping all needed entities, model federation build links
between models and metamodels (even through levels) to make ``things''
work together. As an illustration of this feature, we developed a
free-modeling editor presented
in~\parencite{models2016-freemodel} that frees the designer from the bonds of
model/metamodel conformity. Another notable feature of
this approach is the strong decoupling among tools that remain usable
after federations are made.
So to provide an adaptable framework, we have developed a flexible modeling language offering modeling features without strict modeling levels. In a federation, the targeted modeling approaches can be unknown at the beginning and also can integrate several modeling levels.

@@

      // A basic constructor
      create(String name) { super(name); }
      // Encodes execution of task
      execute() {
        ...
      }
      // Other properties and behaviours of the
      // BPMNTask concept
    }
